### 2024-01-07 doc/Thesis/chapter/04-computational-details.tex
first correction round

\todo{ To me this does not follow any logical order!}
\section{Data Processing}
\label{sec:eval}
\todo{Why this procedure? Sounds quite arbitrary?}
%Reading list
%\begin{itemize}
    %\item https://de.wikipedia.org/wiki/Globaler_F-Test
    %\item https://de.wikipedia.org/wiki/Optimale_Versuchsplanung
    %\item Curse of dimensionality scholar
    %\item linear regression von ungar 
    %\item ridge regression + support vector machine
    %\item correlation vs covariance
    %\item https://en.wikipedia.org/wiki/Regression_analysis
    %\item https://en.wikipedia.org/wiki/Noise_reduction
    %\item https://en.wikipedia.org/wiki/Feature_extraction
    %\item https://en.wikipedia.org/wiki/Feature_selection
    %\item https://en.wikipedia.org/wiki/Dimensionality_reduction
    %\item file:///home/pur/Doc/Uni/Chemie_Master/Int_AIT/Int.git/Code/ML/98_things_can_go_wrong_in_ML_project.html
    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.PCA.html
    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.KernelPCA.html#sklearn.decomposition.KernelPCA
%    \item 
%\end{itemize}
%\td{describe problem and solution found}
\td{Multiple \gls{iv} curves were measured (where are they?)} for every sample.
The main difficulty faced in processing the data was to present the measurements obtained 
from a sample in one representative number. 
%
%\todo{why didn't i just take this?}
%\td{L2 norm because it might be easier to compare to other methods. }
%\td{inspired by euclidean norm/L2 distance from ideal case} 
%\td{wanted to put more weight on bad shunts}
%\td{plot avg, avg(log), avg(log-13)}
%
For every I-V curve (i.e.\,for every aluminium dot contact) the gradient $g$ at $V=0$ (conductance) is calculated by taking 
5 points before and 5 points after the origin with minimum one point distance from zero (which boils
down to the data points from $\pm$\SI{0.02}{\volt} to $\pm$\SI{0.07}{\volt}), 
calculating averages $\overline{V}$ and $\overline{I}$ of each point cloud and taking the ratio of differences:
%averaging their V and I values and calculating
\begin{equation}
    %g = \frac{I_{+m+d} - I_n}{V_{n+1} - V_n}.
    g = \frac{\overline{I}_{+} - \overline{I}_-}{\overline{V}_{+} - \overline{V}_-}
\end{equation}
%
The average of each conductance would be an easy and naive choice but difficult to represent a 
sample correctly since the possible values of conductance span across several magnitudes.
So the average of base 10 logarithm of conductances is the next nearby \textit{ansatz}.
%
In order to make the metric closer 
%and better comparable to the 
\gls{mse} (and to penalize deviation from ideal more than linearly) the average of the squared difference 
to the ideal non-conduction case ($g=10^{-13}$) was chosen instead of the average of logarithms and shall be called conducticity hereafter for lack of a better term. 
%As a measure of conductance a distance $D$ from an ideal non-conducting case. 
%The average of the negative base 10 logarithm subtracted from an ideal non-conducting gradient of $10^{-13}$ 
%and the mean of all conductances was taken
%
\begin{equation}
    \gamma = \sum_i^N \frac{ (-log_{10}(g_i) - 13)^2}{N}
	\label{eq:gamma}
\end{equation}
Another measure is the density of shorted species $\rho$ (pinhole density), calculated in following way:
\begin{equation}
	s_i = \begin{cases}
        1 &\text{if} \quad -log_{10}(g_i) < 5 \\
        0 &\text{if} \quad -log_{10}(g_i) \geq 5 \\
	\end{cases}
\end{equation}
\begin{equation}
	\rho = \sum_i^N \frac{s_i}{N}
	\label{eq:rho}
\end{equation}
The density is 1 if every measurement has a conductance larger than $10^{-5} \, \Omega^{-1}$ and is 0 if every measured conductance has a value of smaller than $10^{-5} \, \Omega^{-1}$.
%Other estimates of the conductance are the averages:
%\begin{equation}
%	G_1 = log \left( \sum_i^N \frac{g_i}{N} \right)
%\end{equation}
%
%\begin{equation}
%	G_2 =  \sum_i^N \frac{log(g_i)}{N}
%%\end{equation}

\section{Sample Selection}
\label{sec:ss}
\todo{for what?}
An evolutionary approach was chosen, namely a multi-objective 
\gls{pso} algorithm called \gls{emma}\cite{villanova2010function,Kennedy1995,Breiman1997,Carta2011}.
%
%"PSO is a population based heuristic inspired by the flocking behavior of birds. 
%To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{villanova2010function}
%
Initially, the input parameters (independent variables), their boundaries and number of equidistant levels for each parameter are declared (see table \ref{tab:input}).
Next, the output variables (dependant variables), their weights in the objective function (the function which should be optimized) are specified and if they should be minimized or maximized is noted.
%
%An initial population of particles, i.e. experiments with certain parameters, is chosen out of the population space (space spanned by all possible combinations of input parameters), 
\begin{table}[htb]
	\centering
	\begin{tabular}{cc cc cc}
		\hline\hline
        $c_{zr}$ [\SI{22}{\milli\mol\per\liter}]	&$\lambda$	&$T_{DB}$[\oc{}]	&$v_{DB}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
		\hline
		2				&4		&40					&10				&300				&120	\\
		3				&6		&50					&12				&400				&360	\\
		4				&8		&60					&14				&500				&600	\\
		5				&10		&70					&16				&					&840	\\
						&12		&80					&18				&					&1080	\\
						&		&					&20				&					&		\\
		\hline\hline
	\end{tabular}
	\caption{Discrete levels of each input parameter }
	\label{tab:input}
\end{table}

The \textit{optimizands} where chosen to be \td{$\gamma$, $\rho$, $\lambda$ and $v_{cal}$, (here it would help me to remind the reader what the symbols are!)}
where $\gamma$, $\rho$ and $\lambda$ are to be minimized and $v_{cal}$ to be maximized.
%which all should be minimized except for $v_{cal}$.
The next step is to generate an initial population (ensemble of experiments), which is chosen randomly from the population space. 
The \td{experiments} are executed, \td{measured (unclear!)} and evaluated according to section 
\ref{sec:exp} and the responses conducticity $\gamma$ (see eq. \ref{eq:gamma}), pinhole density $\rho_s$ (see eq. \ref{eq:rho}), 
\todo{$\lambda$ (numbers of layers) (tstill not clear! what is meant?!)} and $v_{cal}$ (heating rate of calcination process in 
\oc{}/\minutes{}) are supplied to the program. 
The program, then, uses this data to estimate a response for each output variable 
for the entire population space
(and to choose a fraction of the initial population which is allowed to propagate).
%The response variables for the entire population space is calculated. 
The current population - each of the particles independently - 
are given a random velocity vector associated to them, which is directed to the best predicted sample. 
%moves towards the optimum solution.
The population for the next time step is generated and the experiments are again \td{executed, measured and evaluated. (unclear!)}
Each time step thus includes experiment identification, solution preparation, coating deposition and layer analysis.

@@

A grid search over a set of hyperparameters was executed. 
%https://scikit-learn.org/stable/auto_examples/svm/plot_rbf_parameters.html#sphx-glr-auto-examples-svm-plot-rbf-parameters-py
%https://scikit-learn.org/stable/modules/svm.html#svc
% KRR 
The hyperparameters which were examined in \gls{krr} were kernel, $\gamma_{ml}$ and $\alpha$.
The kernel took the form of \gls{rbf}, sigmoid or polynomial with degree 1--3.
The parameters $\alpha$ and $\gamma_{ml}$ (subscript to distinguish from \textit{optimizand}) took the values 0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2, 5 and 10.
%and 0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, respectively.
Note that $\gamma_{ml}$ is used differently in each kernel. 
% SVM
The kernels for \gls{svm} were the same as for \gls{krr}. 
Further hyper parameters were \td{$C$, $\varepsilon$ and $\gamma_{ml}$. 
$C$ and $\varepsilon$ (define again, forgotten until now) } took the values 0.05--1 with step size 0.05 for \gls{svm} and \gls{krr}.
\Gls{svm} additionally used the \texttt{scale} for $\gamma_{ml}$.
%\td{and was the same as for \gls{krr} plus \texttt{scale}.} %$\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 
\texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
and $\sigma(\mathbf{X})$ the variance of the input variables. 
% GRID SEARCH 
The input variables ($c_{zr}$, $\lambda$, $v_{DB}$, $T_{DB}$, $v_{cal}$, $T_{cal}$) 
of the \gls{emma} data set were scaled with the routine \texttt{sklearn.preprocessing.StandardScaler().fit\_transform()}. %\td{scaled before each calculation.}
% https://scikit-learn.org/stable/modules/generated/sklearn.kernel_ridge.KernelRidge.html#sklearn.kernel_ridge.KernelRidge.score
% https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVR.html#sklearn.svm.SVR.score
For each calculation the 5-fold cross-validation score was calculated. 
The score equals to the coefficient of determination $R^2$, which is defined the following for non-linear regression functions:
%\footnote{see https://scikit-learn.org/stable/modules/generated/sklearn.kernel\_ridge.KernelRidge.html\#sklearn.kernel\_ridge.KernelRidge.score}
\footnote{see \href{https://scikit-learn.org/stable/modules/generated/sklearn.kernel\_ridge.KernelRidge.html}{https://scikit-learn.org/stable/modules/generated/sklearn.kernel\_ridge.KernelRidge.html}}
\begin{equation}
	\label{eq:r2}
	R^2 = 1-\frac{\sum (y_i - \hat{y}_i)}{\sum (y_i - \bar{y}_i)}
\end{equation}
For each method (\gls{krr} and \gls{svm}) and each \textit{optimizand} ($\gamma$ and $\rho$) 
the parameters with the highest score were noted.

>>>>

\todo{ To me this does not follow any logical order!}
\section{Data Processing}
\label{sec:eval}
\todo{Why this procedure? Sounds quite arbitrary?}
%Reading list
%\begin{itemize}
    %\item https://de.wikipedia.org/wiki/Globaler_F-Test
    %\item https://de.wikipedia.org/wiki/Optimale_Versuchsplanung
    %\item Curse of dimensionality scholar
    %\item linear regression von ungar 
    %\item ridge regression + support vector machine
    %\item correlation vs covariance
    %\item https://en.wikipedia.org/wiki/Regression_analysis
    %\item https://en.wikipedia.org/wiki/Noise_reduction
    %\item https://en.wikipedia.org/wiki/Feature_extraction
    %\item https://en.wikipedia.org/wiki/Feature_selection
    %\item https://en.wikipedia.org/wiki/Dimensionality_reduction
    %\item file:///home/pur/Doc/Uni/Chemie_Master/Int_AIT/Int.git/Code/ML/98_things_can_go_wrong_in_ML_project.html
    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.PCA.html
    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.KernelPCA.html#sklearn.decomposition.KernelPCA
%    \item 
%\end{itemize}
%\td{describe problem and solution found}
Multiple \gls{iv} curves were measured (see figure \ref{fig:iv}) for every sample.
The main difficulty faced in processing the data was to present the measurements obtained 
from a sample in one representative number. 
%
%\todo{why didn't i just take this?}
%\td{L2 norm because it might be easier to compare to other methods. }
%\td{inspired by euclidean norm/L2 distance from ideal case} 
%\td{wanted to put more weight on bad shunts}
%\td{plot avg, avg(log), avg(log-13)}
%
For every I-V curve (i.e.\,for every aluminium dot contact) the gradient $g$ at $V=0$ (conductance) is calculated by taking 
5 points before and 5 points after the origin with minimum one point distance from zero (which boils
down to the data points from $\pm$\SI{0.02}{\volt} to $\pm$\SI{0.07}{\volt}), 
calculating averages $\overline{V}$ and $\overline{I}$ of each point cloud and taking the ratio of differences:
%averaging their V and I values and calculating
\begin{equation}
    %g = \frac{I_{+m+d} - I_n}{V_{n+1} - V_n}.
    g = \frac{\overline{I}_{+} - \overline{I}_-}{\overline{V}_{+} - \overline{V}_-}
\end{equation}
%
The average of each conductance would be an easy and naive choice but difficult to represent a 
sample correctly since the possible values of conductance span across several magnitudes.
So the average of base 10 logarithm of conductances is the next nearby \textit{ansatz}.
%
In order to make the metric closer 
%and better comparable to the 
\gls{mse} (and to penalize deviation from ideal more than linearly) the average of the squared difference 
to the ideal non-conduction case ($g=10^{-13}$) was chosen instead of the average of logarithms and shall be called conducticity hereafter for lack of a better term. 
%As a measure of conductance a distance $D$ from an ideal non-conducting case. 
%The average of the negative base 10 logarithm subtracted from an ideal non-conducting gradient of $10^{-13}$ 
%and the mean of all conductances was taken
%
\begin{equation}
    \gamma = \sum_i^N \frac{ (-log_{10}(g_i) - 13)^2}{N}
	\label{eq:gamma}
\end{equation}
Another measure is the density of shorted species $\rho$ (pinhole density), calculated in following way:
\begin{equation}
	s_i = \begin{cases}
        1 &\text{if} \quad -log_{10}(g_i) < 5 \\
        0 &\text{if} \quad -log_{10}(g_i) \geq 5 \\
	\end{cases}
\end{equation}
\begin{equation}
	\rho = \sum_i^N \frac{s_i}{N}
	\label{eq:rho}
\end{equation}
The density is 1 if every measurement has a conductance larger than $10^{-5} \, \Omega^{-1}$ and is 0 if every measured conductance has a value of smaller than $10^{-5} \, \Omega^{-1}$.
%Other estimates of the conductance are the averages:
%\begin{equation}
%	G_1 = log \left( \sum_i^N \frac{g_i}{N} \right)
%\end{equation}
%
%\begin{equation}
%	G_2 =  \sum_i^N \frac{log(g_i)}{N}
%%\end{equation}

\section{Evolutionary Model-based Multiresponse Approach}
\label{sec:ss}
%\todo{for what?}
An evolutionary approach was chosen, namely a multi-objective 
\gls{pso} algorithm called \gls{emma}\cite{villanova2010function,Kennedy1995,Breiman1997,Carta2011}.
%
%"PSO is a population based heuristic inspired by the flocking behavior of birds. 
%To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{villanova2010function}
%
Initially, the input parameters (independent variables), their boundaries and number of equidistant levels for each parameter are declared (see table \ref{tab:input}).
Next, the output variables (dependant variables), their weights in the objective function (the function which should be optimized) are specified and if they should be minimized or maximized is noted.
%
%An initial population of particles, i.e. experiments with certain parameters, is chosen out of the population space (space spanned by all possible combinations of input parameters), 
\begin{table}[htb]
	\centering
	\begin{tabular}{cc cc cc}
		\hline\hline
        $c_{zr}$ [\SI{22}{\milli\mol\per\liter}]	&$\lambda$	&$T_{C}$[\oc{}]	&$v_{C}$[\mm{}/\s{}]	&$T_{cal}$[\oc{}]	&$v_{cal}$[\oc{}/\h{}]	\\
		\hline
		2				&4		&40					&10				&300				&120	\\
		3				&6		&50					&12				&400				&360	\\
		4				&8		&60					&14				&500				&600	\\
		5				&10		&70					&16				&					&840	\\
						&12		&80					&18				&					&1080	\\
						&		&					&20				&					&		\\
		\hline\hline
	\end{tabular}
	\caption{Discrete levels of each input parameter }
	\label{tab:input}
\end{table}

The \textit{optimizands} where chosen to be $\gamma$, $\rho$, $\lambda$ and $v_{cal}$, 
(i.e. conducticity, pinhole density, coating layer count and heating rate)
where $\gamma$, $\rho$ and $\lambda$ are to be minimized and $v_{cal}$ to be maximized.
%which all should be minimized except for $v_{cal}$.
The next step is to generate an initial population (ensemble of experiments), which is chosen randomly from the population space. 
The samples are produced, the \gls{iv} curves are measured and measurements evaluated according to section 
\ref{sec:exp} and the responses conducticity $\gamma$ (see eq. \ref{eq:gamma}), pinhole density $\rho_s$ (see eq. \ref{eq:rho}), 
$\lambda$ (numbers of coating layers) and $v_{cal}$ (heating rate of calcination process in 
\oc{}/\minutes{}) are supplied to the program. 
The program, then, uses this data to estimate a response for each output variable 
for the entire population space
(and to choose a fraction of the initial population which is allowed to propagate).
%The response variables for the entire population space is calculated. 
The current population - each of the particles independently - 
are given a random velocity vector associated to them, which is directed to the best predicted sample. 
%moves towards the optimum solution.
The population for the next time step is generated and 
again the samples are produced, the \gls{iv} curves are measured and measurements evaluated.
%the experiments are again \td{executed, measured and evaluated. (unclear!)}
Each time step thus includes experiment identification, solution preparation, coating deposition and layer analysis.

@@

A grid search over a set of hyperparameters was executed. 
%https://scikit-learn.org/stable/auto_examples/svm/plot_rbf_parameters.html#sphx-glr-auto-examples-svm-plot-rbf-parameters-py
%https://scikit-learn.org/stable/modules/svm.html#svc
% KRR 
The hyperparameters which were examined in \gls{krr} were kernel, $\gamma_{ml}$  and $\alpha$ (regularization parameter).
The kernel took the form of \gls{rbf}, sigmoid or polynomial with degree 1--3.
The parameters $\alpha$ and $\gamma_{ml}$ (subscript to distinguish from \textit{optimizand}) took the values 0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2, 5 and 10.
Note that $\gamma_{ml}$ is used differently in each kernel.

% SVM
The kernels for \gls{svm} were the same as for \gls{krr}. 
\Gls{svm} uses $C$ instead of $\alpha$ as regularization parameter) and  $\varepsilon$ as \gls{svm} tube size parameter.
$C$ and $\varepsilon$ took the values 0.05--1 with step size 0.05. 
\Gls{svm} additionally used the \texttt{scale} for $\gamma_{ml}$.
\texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
and $\sigma(\mathbf{X})$ the variance of the input variables.

% GRID SEARCH 
The input variables ($c_{zr}$, $\lambda$, $v_{C}$, $T_{C}$, $v_{cal}$, $T_{cal}$) 
of the \gls{emma} data set were scaled with the routine \texttt{sklearn.preprocessing.StandardScaler().fit\_transform()}. %\td{scaled before each calculation.}
% https://scikit-learn.org/stable/modules/generated/sklearn.kernel_ridge.KernelRidge.html#sklearn.kernel_ridge.KernelRidge.score
% https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVR.html#sklearn.svm.SVR.score
For each calculation the 5-fold cross-validation score was calculated. 
The score equals to the coefficient of determination $R^2$, which is defined the following for non-linear regression functions:
%\footnote{see https://scikit-learn.org/stable/modules/generated/sklearn.kernel\_ridge.KernelRidge.html\#sklearn.kernel\_ridge.KernelRidge.score}
\footnote{see \href{https://scikit-learn.org/stable/modules/generated/sklearn.kernel\_ridge.KernelRidge.html}{https://scikit-learn.org/stable/modules/generated/sklearn.kernel\_ridge.KernelRidge.html}}
\begin{equation}
	\label{eq:r2}
	R^2 = 1-\frac{\sum (y_i - \hat{y}_i)}{\sum (y_i - \bar{y}_i)}
\end{equation}
For each method (\gls{krr} and \gls{svm}) and each \textit{optimizand} ($\gamma$ and $\rho$) 
the parameters with the highest score were noted.
